Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-07-07 Latex/journal_v1/V5/pr.tex
add figure to journal

 %\pdfoutput=1
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{mathtools}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\usepackage[export]{adjustbox}
\setlength{\columnsep}{11mm}
\begin{document}

\title{Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
  \author{
    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
    \vspace{-.2cm}
  }
  }

@@

\begin{figure*}
  \centering 
    \includegraphics[scale = 0.5]{Drawing14.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{Drawing14.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure*}
The rest of this paper is organized as follow. The system model and the problem formulation is described 
in Section \ref{systemmodel}. The details of our proposed resource management algorithm is 
introduced in Seection \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Section \ref{conc}, concludes the whole paper.

@@

In this section, first, we  present the system model. Then, we obtain achievable data rates, power of O-RU and the fronthaul capacity for the downlink (DL) of the ORAN system. Afterward, we discuss about the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
Suppose we have three service types includes mMTC, eMBB and URLLC which support different applications.

@@

\section{Numerical Result}\label{NE}

>>>>

 %\pdfoutput=1
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{mathtools}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\usepackage[export]{adjustbox}
\setlength{\columnsep}{11mm}
\begin{document}

\title{Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
  \author{
    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
    \vspace{-.2cm}
  }
  }

@@

\begin{figure*}
  \centering 
    \includegraphics[scale = 0.75]{finalDraw.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure*}

The rest of this paper is organized as follow. The system model and the problem formulation is described 
in Section \ref{systemmodel}. The details of our proposed resource management algorithm is 
introduced in Seection \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Section \ref{conc}, concludes the whole paper.

@@

In this section, we describe the downlink system in O-RAN slicing as depicted in Figure \ref{fig:c11}. 
Here, firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU and the fronthaul capacity for the downlink (DL) of the ORAN system. Afterward, we discuss about the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
Suppose we have three service types includes mMTC, eMBB and URLLC which support different applications.

@@

\section{Numerical Results}\label{NE}
In this section, numerical results for the problem are depicted to evaluate the performance of the algorithms.
